Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-17 cosmic_voids.tex
5.3.1 Density profiles of voids, done

We choose an integration radius of $R=4r_{eff}$, that is large enough to 
enclose the compensation ridge for a typical void in case there is one. 
This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
constituting the family of overcompensated voids. These voids generally 
exhibit a compensation ridge associated to dense nearby structures. In the 
same fashion, voids with $\mathcal{C}<1$ constitute the family of 
subcompensated voids.

@@

Since the shape of the voids exhibit a wide range of geometries, a common 
way to represent their size is through the equivalent spherical radius or
effective radius, defined as $r_{eff} = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void. As mentioned before, we applied a threshold merger
in order to avoid void hierarchization, what means we are working with the
top hierarchy of voids. We limit our findings to voids with effective radius
greater than the smoothing length of the density field, i.e. $\sim 1$\hMpc. 
Below that scale numerical resolution effects becomes important. We find a
volume filling fraction of voids of $54.88\%$ of the total volume of the 
simulation for the FA-Tweb and $47.06\%$ for the FA-Vweb.

@@

For both schemes overcompensated voids are more abundant, however at 
larger scales abundances of subcompensated voids become comparable. This 
is somehow expected as larger voids are more likely to abut other voids.
A recent estimation of the radius of the local void gives $r_{LV}\approx
10$ Mpc \citep{Nasonova11}. Taking the dimensionless Hubble constant as 
$h = 0.70$, the size of the local void would be around $r_{eff} = 7$
\hMpc\ in the shown distribution. For both schemes, this places the local
void as a rather common void in terms of size, and more likely to be
overcompensated.

@@

In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
voids. We calculate the contrast density, radial-projected velocity and 
FA profiles. For this purpose we catalogue all the voids into several 
radial bins in order to capture possible size effects. Then, for each void, 
we take the distance of each member cell to the void centre along with the 
properties of interest. Normalizing these distances with the effective 
radius, we stack all the voids catalogued in a radial bin in order to 
compute radial profiles of the properties of interest.

@@

In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
voids. We calculate the contrast density, radial-projected velocity and 
FA profiles. For this purpose we catalogue all the voids into several 
radial bins in order to capture possible size effects. Then, for each void, 
we take the distance of each member cell to the void centre along with the 
properties of interest. Normalizing these distances with the effective 
radius, we stack all the voids catalogued in a radial bin in order to 
compute radial profiles of the properties of interest.

>>>>

We choose an integration radius of $R=4\reff$, that is large enough to 
enclose the compensation ridge for a typical void in case there is one. 
This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
constituting the family of overcompensated voids. These voids generally 
exhibit a compensation ridge associated to dense nearby structures. In the 
same fashion, voids with $\mathcal{C}<1$ constitute the family of 
subcompensated voids.

@@

Since the shape of the voids exhibit a wide range of geometries, a common 
way to represent their size is through the equivalent spherical radius or
effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void. As mentioned before, we applied a threshold merger
in order to avoid void hierarchization, what means we are working with the
top hierarchy of voids. We limit our findings to voids with effective radius
greater than the smoothing length of the density field, i.e. $\sim 1$\hMpc. 
Below that scale numerical resolution effects becomes important. We find a
volume filling fraction of voids of $54.88\%$ of the total volume of the 
simulation for the FA-Tweb and $47.06\%$ for the FA-Vweb.

@@

For both schemes overcompensated voids are more abundant, however at 
larger scales abundances of subcompensated voids become comparable. This 
is somehow expected as larger voids are more likely to abut other voids.
A recent estimation of the radius of the local void gives $r_{LV}\approx
10$ Mpc \citep{Nasonova11}. Taking the dimensionless Hubble constant as 
$h = 0.70$, the size of the local void would be around $\reff = 7$
\hMpc\ in the shown distribution. For both schemes, this places the local
void as a rather common void in terms of size, and more likely to be
overcompensated.

@@

In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
voids. We calculate the contrast density, radial-projected velocity and 
FA profiles. For this purpose we catalogue all the voids in several radial 
bins in order to capture possible size effects; moreover we show profiles 
for both, subcompensated and overcompensated voids. Then, for each void, 
we take the distance of each member cell to the void centre along with the 
properties of interest. Normalizing these distances with the effective 
radius, we stack all the voids of a radial bin in order to compute the 
radial profiles.

@@

In left panels of Fig. \ref{fig:RhoVel} we compute density profiles of 
voids stacked according to their size and their compensation index. 
Instead of calculating the radial internal structure inside an effective
radius, we opted for a radius well beyond that value ($8\ \reff$) in order 
to capture the properties of neighbour structures as well.

A first interesting result is the value at the void centres: the larger the 
void, the more underdense their value at the centre, ranging from $\delta
\approx-0.95$ for the largest voids ($8.3-12\ \hMpc$) to $\delta\approx 
-0.8$ for the smallest voids ($2-3.2\ \hMpc$). This holds for all the voids 
in both schemes. These very low values are consistent with most of the void 
finding schemes based on smooth and continuous fields from simulation or 
reconstruction procedures on surveys \citep{Plionis02, Colberg05, Shandarin06, 
Platen07, Neyrinck08, MunozCuartas11, Neyrinck13, Ricciardelli2013}, unlike
geometrical approaches based on point distributions, where central values
are generally higher \citep{Colberg08}.

Another important result is the steepness of the profiles at inner
regions. For subcompensated voids, larger voids are more steep, reaching
the mean density value at lower radius. Smaller voids exhibit moderate
slopes, reaching the mean density at much larger radius. This indicates 
smaller subcompensated voids are embedded into low density structures like 
larger voids and still forming regions like walls. For subcompensated large
voids, outer radial layers are so vast that all sort of structures are 
stacked, thus reaching the mean density at lower radius. This result 
remains also for overcompensated voids, where larger voids reach first 
both, the compensation ridge and then the mean density value.

Regarding overcompensated voids, a final result is related to the height 
of the compensation ridge: the larger the void size, the lower the ridge
height. This implies that overcompensated smaller voids are embedded in 
very high density regions, unlike their subcompensated counterpart, thus 
indicating two possibly different processes for small voids formation. 
Larger voids exhibit lower ridges as outer radial layers also includes all
sort of structures, thus being the difference between large overcompensated
and subcompensated voids less conclusive.

All the previous results hold for both finding schemes, thereby pointing 
out to an universal radial profile of voids (subcompensated and 
overcompensated), and not only for the internal structure \citep{Colberg05, 
Ricciardelli2013}, but also for outer regions \citep{Lavaux12, Hamaus14}.
